Continous time Markov chain models; \\ extension, simulation and visualisation

### 2014-10-13 chapters/chapter01.tex
figures

%bayesian
The advent of powerfull and increasingly more attainable compute power has been instrumental to the adoption of statistical methods based on likleihood estimation and very closely realted Bayesian methods.
Bayesian statistics are not a new idea, stemming back to the 18th century and the works of reverend Thomas Bayes, a statistician, philosopher and theologian.

%---BAYES---%
\begin{figure}[H]
\centering
\includegraphics[scale=0.4]{Thomas_Bayes} 
\caption{
{ \footnotesize 
{\bf Only known portrait of reverend Thomas Bayes.} This portrait was published in the 1936 book on the history of actuarial science `History of Life Insurance'. It is only hypothesised to be an actual portrait of the scholar.
}% END: footnotesize
}
\label{fig:bayes}
\end{figure}

>>>>

%bayesian
The advent of powerfull and increasingly more attainable compute power has been instrumental to the adoption of statistical methods based on likelihood estimation and very closely realted Bayesian methods.
Bayesian statistics are not a new idea, stemming back to the 18th century and the works of reverend Thomas Bayes, a statistician, philosopher and theologian.

%---BAYES---%
\begin{remark}{Thomas Bayes}
\begin{figure}[H]
\centering
\includegraphics[scale=0.4]{Thomas_Bayes} 
\caption{
{ \footnotesize 
{\bf Only known portrait of reverend Thomas Bayes.} This portrait was published in the 1936 book on the history of actuarial science `History of Life Insurance'. It is only hypothesised to be an actual portrait of the scholar.
}% END: footnotesize
}
\label{fig:bayes}
\end{figure}
\end{remark}
